Exploring dimensions of biodiversity in Japanese ferns

### 2020-06-30 ms/SI.Rmd
Change k for phylo bioregions from 7 to 6
Add k plot for ecostructure

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, results = "hide", cache = TRUE)
```

@@

loadd(list = c(
  "occ_point_data_ferns",
  "ses_phy_ferns",
  "ses_phy_ferns_endemic",
  "ses_traits_ferns",
  "shape_ferns",
  "k_taxonomy",
  "k_phylogeny",
  "regions_taxonomy",
  "regions_phylogeny",
  "species_motifs_ferns"
),
cache = ja_fern_cache)

@@

k_phylogeny_select <- 7

@@

<!-- (Add k plot for ecostructure) -->

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, results = "hide", cache = FALSE)
```

@@

loadd(list = c(
  "occ_point_data_ferns",
  "ses_phy_ferns",
  "ses_phy_ferns_endemic",
  "ses_traits_ferns",
  "shape_ferns",
  "k_taxonomy",
  "k_phylogeny",
  "regions_taxonomy",
  "regions_phylogeny",
  "species_motifs_ferns",
  "species_motifs_ferns_combined"
),
cache = ja_fern_cache)

@@

k_phylogeny_select <- 6

@@

```{r k-plot-ecos, fig.width = 4, fig.height = 3}
# Extract log likelihoods for each value of K from ecostructure results
log_l <- map_dbl(species_motifs_ferns_combined, ~pluck(., "L")) %>%
  tibble(k = names(.) %>% parse_number, log_l = .) %>%
  mutate(
    optimal_manual = ifelse(k == k_taxonomy_select, TRUE, FALSE)
  )

ggplot(log_l, aes(x = k, y = log_l)) +
  geom_line() +
  geom_point(aes(color = optimal_manual), size = 2.5) +
  scale_color_manual(values = c("TRUE" = "#E31A1C", "FALSE" = "black")) +
  labs(
    y = "Log likelihood",
    x = "Number of clusters") +
  theme(legend.position = "none")

ggsave(result_file("k-plot-ecos", "pdf"), width = 4, height = 3, units = "in")
```

**`r s_figure("k-plot-ecos")`**. `r s_figure_cap("k-plot-ecos")` Red indicates optimal *k* selected manually (*k* = 8, same as for taxonomic bioregions).

### 2020-06-30 ms/manuscript.Rmd
Add k plot for ecostructure

We analyzed ecological structure using the framework of @White2019 and their R package \package{ecostructure}. This method involves fitting the community matrix to a grade of membership model, which allows communities have partial membership in multiple groups [@White2019]. Like bioregion analysis, this method also requires selecting the number of clusters (in this context called "motifs" after @White2019) to fit the model. We initially tested values of *k* from 1 to 20 and inspected the log-likelihood for each, but found that it continually improved without reaching a clear optimum. We therefore used the same *k* that was selected for taxonomic bioregions.

>>>>

We analyzed ecological structure using the framework of @White2019 and their R package \package{ecostructure}. This method involves fitting the community matrix to a grade of membership model, which allows communities have partial membership in multiple groups [@White2019]. Like bioregion analysis, this method also requires selecting the number of clusters (in this context called "motifs" after @White2019) to fit the model. We initially tested values of *k* from 2 to 20 and inspected the log-likelihood for each, but found that it continually improved without reaching a clear optimum (`r s_figure("k-plot-ecos")`). We therefore used the same *k* that was selected for taxonomic bioregions.
